General purpose gene annotation using deep learning

### 2020-04-20 paper/main.tex
minor

\begin{methods}
\section{Methods}
We worked with 192 animal and 60 plant genomes. The data of each genome consists of the latest publically available genomic assembly in form of a FASTA file and the latest annotation in the GFF format. We used all animals genomes in EnsemblMetazoa 45 (\citealp{Howe19}) as well as all non-embargoed plant genomes of the JGI Phytosome 13 database (\citealp{Phytozome}). Both data groups were used seperately during training as well as during evaluation. At the start of our work we split both genome groups into {\it training genomes} and {\it test genomes}. The test genome group is made up of 19 or 6 genomes, respectively, and was chosen to be of the best possible quality based on collected metadata while also representing a broad phylogenetic spread. We then experimented which genomes to use for during training from the pool of training genomes while evaluating the performance of models on the remaining ones. We call the genomes that were ultimatily not used during training the {\it validation genomes}. While we did split off a group of test genomes at the beginning of our work, we ended up only reporting on the generalization performance of the combined set of validation and test genomes as the validation genomes are by far the largest set. We also do not find a noticible difference in performance between those two groups.

>>>>

\begin{methods}
\section{Methods}
We worked with 192 animal and 60 plant genomes. The data of each genome consists of the latest publically available genomic assembly in form of a FASTA file and the latest annotation in the GFF format. We used all animals genomes in EnsemblMetazoa 45 (\citealp{Howe19}) as well as all non-embargoed plant genomes of the JGI Phytosome 13 database (\citealp{Phytozome}). Both data groups were used seperately during training as well as during evaluation. At the start of our work we split both genome groups into {\it training genomes} and {\it test genomes}. The test genome group is made up of 19 and 6 genomes, respectively, and was chosen to be of the best possible quality based on collected metadata while also representing a broad phylogenetic spread. We then experimented which genomes to use for during training from the pool of non-test genomes while evaluating the performance of models on the remaining ones. We call the genomes that were ultimatily not used during training the {\it validation genomes}. While we did split off a group of test genomes at the beginning of our work, we ended up only reporting on the generalization performance of the combined set of validation and test genomes as the validation genomes are by far the largest set. We also do not find a noticible difference in performance between those two groups.
